---
title: "Supplementary materials: Associations between daily composition of 24-hour physical behavior with affective states and working memory"
author: "Flora Le (flora.le@monash.edu)"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 10
    fig_height: 4
    fig_caption: yes
    number_sections: true
---

This file presents the full 
results for the analysis of
**Associations between daily composition of 24-hour physical behavior with affective states and working memory**.

*Notes.* 
Statistical significance of individual parameters was set as Bayesian 95% posterior credible intervals (CIs) not including zero. Sleep = Sleep Period. MVPA = Moderate-to-Vigorous Physical Activity. LPA = Light Physical Activity.

```{r, echo=FALSE, message=FALSE}
source("emia-24h-affect-wm-supp.R")
```

# Concurrent results 
## 60-minute reallocations
 * Reallocation of 60 minutes between movement behaviours and *valence*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_60_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#E9E6F1")
```

 * Reallocation of 60 minutes between movement behaviours and *energetic arousal*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_60_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Reallocation of 60 minutes between movement behaviours and *calmness*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_60_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF4E8")
```

 * Reallocation of 60 minutes between movement behaviours and *working memory performance*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_60_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#F5E1D5")
```

## 30-minute reallocations

 * Reallocation of 30 minutes between movement behaviours and *valence*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_30_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#E9E6F1")
```

 * Reallocation of 30 minutes between movement behaviours and *energetic arousal*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_30_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Reallocation of 30 minutes between movement behaviours and *calmness*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_30_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF4E8")
```

 * Reallocation of 30 minutes between movement behaviours and *working memory performance*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_30_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#F5E1D5")
```

## 5-minute reallocations

 * Reallocation of 5 minutes between movement behaviours and *valence*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_5_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#E9E6F1")
```

 * Reallocation of 5 minutes between movement behaviours and *energetic arousal*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_5_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Reallocation of 5 minutes between movement behaviours and *calmness*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_5_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF4E8")
```

 * Reallocation of 5 minutes between movement behaviours and *working memory performance*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_sub_5_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#F5E1D5")
```


## Visualisation of reallocations from 1 to 60 minutes

*Notes.* Significance at a: 5 minutes, b: 30 minutes, and c: 60 minutes.

### Between person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(emia_24h_plot_b_supp, print)
```

### Within person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(emia_24h_plot_w_supp, print)
```


# Prospective results 
## 60-minute reallocations
 * Reallocation of 60 minutes between movement behaviours and *valence*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_60_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#E9E6F1")
```

 * Reallocation of 60 minutes between movement behaviours and *energetic arousal*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_60_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Reallocation of 60 minutes between movement behaviours and *calmness*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_60_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF4E8")
```

 * Reallocation of 60 minutes between movement behaviours and *working memory performance*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_60_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#F5E1D5")
```

## 30-minute reallocations

 * Reallocation of 30 minutes between movement behaviours and *valence*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_30_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#E9E6F1")
```

 * Reallocation of 30 minutes between movement behaviours and *energetic arousal*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_30_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Reallocation of 30 minutes between movement behaviours and *calmness*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_30_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF4E8")
```

 * Reallocation of 30 minutes between movement behaviours and *working memory performance*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_30_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#F5E1D5")
```

## 5-minute reallocations

 * Reallocation of 5 minutes between movement behaviours and *valence*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_5_list[[1]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#E9E6F1")
```

 * Reallocation of 5 minutes between movement behaviours and *energetic arousal*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_5_list[[2]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#CBD5D0")
```

 * Reallocation of 5 minutes between movement behaviours and *calmness*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_5_list[[3]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#FAF4E8")
```

 * Reallocation of 5 minutes between movement behaviours and *working memory performance*
 
```{r, warning=FALSE, echo=FALSE}
kbl(emia_24h_lead_sub_5_list[[4]], align = "l", espacce = F) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"), fixed_thead = T) %>%
  row_spec(0, background = "#F5E1D5")
```


## Visualisation of reallocations from 1 to 60 minutes

*Notes.* Significance at a: 5 minutes, b: 30 minutes, and c: 60 minutes.

### Between person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(emia_24h_lead_plot_b_supp, print)
```

### Within person level

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
walk(emia_24h_lead_plot_w_supp, print)
```
